مفاهیم اولیه بلاک چین

### 2024-01-25 papers/main.tex
udpate paper with last chain

>>>>

محتوای بلاک چین زیر به صورت شبیه‌سازی شده، به شکل زیر می‌باشد:

\begin{LTR}
    \begin{lstlisting}
    [
        {
            "timestamp": "Genesis time",
            "transactions": [
                "Genesis block"
            ],
            "previousHash": "Genesis block",
            "hash": "ed46325cd9a7f383fd982770d2acc70712115e98f690225810bbf0dcd7d54783",
            "nonce": 1,
            "validator": "Genesis block",
            "signature": "Genesis block"
        },
        {
            "timestamp": "1706167941159",
            "transactions": [],
            "previousHash": "ed46325cd9a7f383fd982770d2acc70712115e98f690225810bbf0dcd7d54783",
            "hash": "5a7e6c1d226f002b9e6cd7266a2f3492f59a3a44ee42e9bd61aacf09a3f370de",
            "nonce": 1,
            "validator": "",
            "signature": ""
        },
        {
            "timestamp": "1706168456124",
            "transactions": [],
            "previousHash": "5a7e6c1d226f002b9e6cd7266a2f3492f59a3a44ee42e9bd61aacf09a3f370de",
            "hash": "464a15adc7be56d1c3d10e06efb93e1c5a725f240685b1e74f92eaf4e405862c",
            "nonce": 1,
            "validator": "",
            "signature": ""
        }
    ]
    \end{lstlisting}
\end{LTR}
